Foraging: The Triumphant Return

### 2022-06-07 manuscript.tex
Updates from Overleaf

% Keywords
\keyword{foraging; visual search; bayesian model; decision; strategy (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}

@@

To test how well our methods generalise, we will introduce a new dataset that was not analysed in our previous modelling paper....

@@

\begin{itemize}
    \item $b_A$ - preference for selecting items of type $A$ rather than $B$.
    \item $b_S$ - preference for selections items of the same type as the previously selected item.
    \item $\sigma_d$ - preference for selecting items close to the previously selected item.
    \item $\sigma_{\theta}$ - preference to keep selecting items along a straight line versus changing direction.
\end{itemize}

@@

One weakness of the foraging model by \cite{clarke2022foraging} is that it makes little attempt to the predict which item will be selected first. In this section we aim to improve this by modelling participant bias/preference in their choice of initial target selection. Following \cite{clarke_tatler2014, clarke2017} we fit truncated Gaussian distributions to the $(x,y)$ coordinates of the initial target selections

Figure \ref{fig:qjep_init_sel_hex} shows the distribution of the locations of first target selections. We can see that unlike the central bias in fixations during scene viewing, the distribution of initial target locations appear to be bimodal: while most targets are positioned in the top left hand corner <CHECK MATLAB CODE!!!> there is a second smaller distribution of central target selections. This appears to be due to different participants choosing to utilise different strategies rather than within-subject variation. However, we have no evidence that these different initial strategies affect the model parameters in any systematic way (see Supplementary Material)

@@

\subsection{Multi-level Modelling Results}
We modelled this bias using a multi-level two-dimensional $[0, 1]$ truncated Gaussian distribution, the results of which are shown in Figure \ref{fig:qjep_init_sel_mdl}\footnote{Full details of the analysis can be found in the supplementary materials}.

@@

>>>>

% Keywords
\keyword{foraging; visual search; bayesian model; decision; strategy.}

@@

To test how well our methods generalise, we use the dataset from \citep{kristjansson2014}. We split this into a training dataset (50\% of the original data i.e. 10 trials per participant) and a test dataset (the remaining 50\% of the data). The foraging model is fit on the training dataset, and the parameters from this model are then used to predict behaviour at the level of individual trials. We show that our methods appear to generalise beyond \citep{clarke2022}: further details can be found in the \textit{Supplementary Materials}.

@@

\begin{itemize}
    \item $b_A$ - preference for selecting items of type $A$ rather than $B$.
    \item $b_S$ - preference for selecting items of the same type as the previously selected item.
    \item $\sigma_d$ - preference for selecting items close to the previously selected item.
    \item $\sigma_{\theta}$ - preference to keep selecting items along a straight line versus changing direction.
\end{itemize}

@@

One weakness of the foraging model by \cite{clarke2022foraging} is that it makes little attempt to predict which item will be selected first. In this section we aim to improve this by modelling participant bias (or preference) in their choice of initial target selection. Following \cite{clarke_tatler2014, clarke2017} we fit truncated Gaussian distributions to the $(x,y)$ coordinates of the initial target selections.

Figure \ref{fig:qjep_init_sel_hex} shows the distribution of the locations of first target selections. We can see that unlike the central bias in fixations during scene viewing, the distribution of initial target locations appear to be bimodal: while most targets are positioned in the top left hand corner, there is a second smaller distribution of central target selections. This appears to be due to different participants choosing to utilise different strategies rather than within-subject variation. However, we have no evidence that these different initial strategies affect the model parameters in any systematic way (see \textit{Supplementary Material}).

@@

\subsection{Multi-level Modelling Results}
We modelled this bias using a multi-level two-dimensional $[0, 1]$ truncated Gaussian distribution, the results of which are shown in Figure \ref{fig:qjep_init_sel_mdl}\footnote{Full details of the analysis can be found in the \textit{Supplementary Materials}}.

@@

\begin{figure}[H]
\centering
\includegraphics[width=12 cm]{Figures/init_sel2_mdl.pdf}
\caption{Posterior fits for (\textit{left}) horizontal and (\textit{middle}) vertical locations of the initial target selection. Each line represents a different participant.  (\textit{right}) shows the correlation between participant's mean $x$ and $y$ coordinates. The box shows the extent of the stimulus.}
\label{fig:qjep_init2_sel_mdl}
\end{figure}
